---
title: "Regional DataBase Estimation System data call"
author:
  - Mathieu Depetris^[IRD, mathieu.depetris@ird.fr]
date: "28/09/2023"
output: rmarkdown::html_vignette
description: |
  Description of Regional DataBase Estimation System data call.
vignette: |
  %\VignetteIndexEntry{Regional DataBase Estimation System data call}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<div style="text-align: justify">

## Regional DataBase Estimation System data call

The Regional DataBase and Estimation System, RDBES, is the new regional database currently being developed by ICES. This system is a structure hosting a database but also processes and treatments, for example with an aim of data validation and quality. The aims of the RDBES are:

* To ensure that data can be made available for the coordination of regional fisheries data sampling plans, in particular for the EU DC-MAP Regional Coordination Groups (RCGs),
* To provide a regional estimation system such that statistical estimates of quantities of interest can be produced from sample data,
* To increase the data quality, documentation of data and ensuring of approved estimation methods are used,
* To serve and facilitate the production of fisheries management advice and status reports,
* To increase the awareness of fisheries data collected by the users of the RDBES and the overall usage of these data.

More information is available on the [GitHub](https://github.com/ices-tools-dev/RDBES/tree/master) or on the [offical webpage](https://rdbes.ices.dk/#/home).

## 2023 version

Github tag for scripts apply in 2023: 

Github 2023 documentation associated:

To compile it on your computer use the following code:

```{r, eval = FALSE, echo = TRUE}
devtools::install_github("OB7-IRD/acdc@vx.x.x",
                         INSTALL_opts=c("--no-multiarch"))
```

Specific configuration and parameters is available below:

```{r, eval = FALSE, echo = TRUE}
# setup ----
library(furdeb)
library(acdc)
config <- configuration_file(path_file = "D:/bdd/rdbes/data_call/2023/rdbes_datacall_2023_configuration_file.yml",
                             silent = TRUE)
# parameters definition ----
year_time_period <- 2022L
# for the French fleet, 1 = France
flag <- 1L
major_fao_area_filter <- as.integer(x = c(21, 27, 34, 41, 47, 87))
digit_accuracy <- 1L
hash_algorithms <- "crc32"
encrypted_vessel_code_separator <- ";"
fao_area_file_path <- "D:/developpement/shapes/FAO_AREAS_CWP_NOCOASTLINE/FAO_AREAS_CWP_NOCOASTLINE.Rdata"
eez_area_file_path <- "D:/developpement/shapes/Intersect_EEZ_IHO_v4_2020/Intersect_EEZ_IHO_v4_2020.Rdata"
export_path <- config$output_path
# databases connections ----
balbaya_con <- postgresql_dbconnection(db_user = config[["databases_configuration"]][["balbaya_vmot5"]]$login,
                                       db_password = config[["databases_configuration"]][["balbaya_vmot5"]]$password,
                                       db_dbname = config[["databases_configuration"]][["balbaya_vmot5"]]$dbname,
                                       db_host = config[["databases_configuration"]][["balbaya_vmot5"]]$host,
                                       db_port = config[["databases_configuration"]][["balbaya_vmot5"]]$port)
observe_con <- postgresql_dbconnection(db_user = config[["databases_configuration"]][["observe_vmot6_test"]]$login,
                                       db_password = config[["databases_configuration"]][["observe_vmot6_test"]]$password,
                                       db_dbname = config[["databases_configuration"]][["observe_vmot6_test"]]$dbname,
                                       db_host = config[["databases_configuration"]][["observe_vmot6_test"]]$host,
                                       db_port = config[["databases_configuration"]][["observe_vmot6_test"]]$port)
# data call tables generation ----
table_cl <- rdbes_cl(observe_con = observe_con,
                     balbaya_con = balbaya_con,
                     fao_area_file_path = fao_area_file_path,
                     eez_area_file_path = eez_area_file_path,
                     year_time_period = year_time_period,
                     flag = flag,
                     major_fao_area_filter = major_fao_area_filter,
                     digit_accuracy = digit_accuracy,
                     hash_algorithms = hash_algorithms,
                     encrypted_vessel_code_separator = encrypted_vessel_code_separator,
                     export_path = export_path)

table_ce <- rdbes_ce(observe_con = observe_con,
                     balbaya_con = balbaya_con,
                     fao_area_file_path = fao_area_file_path,
                     eez_area_file_path = eez_area_file_path,
                     year_time_period = year_time_period,
                     flag = flag,
                     major_fao_area_filter = major_fao_area_filter,
                     hash_algorithms = hash_algorithms,
                     encrypted_vessel_code_separator = encrypted_vessel_code_separator,
                     export_path = export_path)

table_vd <- rdbes_vd(observe_con,
                     rdbes_table_cl = table_cl,
                     rdbes_table_ce = table_ce,
                     flag = flag,
                     hash_algorithms = hash_algorithms,
                     encrypted_vessel_code_separator = encrypted_vessel_code_separator,
                     export_path = export_path)

table_sl <- rdbes_sl(rdbes_table_cl = table_cl,
                     export_path = export_path)
```

## Global comments for further development and improvement

Theses comments aims to highlight every subjects or topics related to the future improvement of the large pelagics data integration in the RDBES. For more information and detail please contact [Mathieu Depetris](mathieu.depetris@ird.fr).

### Table CL: Commercial Landing

To do

### Table CE: Commercial Effort

To do

### Table VD: Vessel Details

To do

### Table SL: Species List

To do




